\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix typo

Many protocols suffer from the lack of an endogenous financing mechanism, and stateless protocols cannot have them by definition. Even in many stateful protocols, key contributors end up either severly underfunded, which is detrimental to quality and development progress, or they rely on third part revenue sources which do not have incentives that are guided by the interests of all protocol stakeholders.

>>>>

Many protocols suffer from the lack of an endogenous financing mechanism, and stateless protocols cannot have them by definition. Even in many stateful protocols, key contributors end up either severly underfunded, which is detrimental to quality and development progress, or they rely on third party revenue sources which do not have incentives that are guided by the interests of all protocol stakeholders.
